% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      
    First and foremost, I would like to express my deepest gratitude 
    to my supervisor, Terry Wyatt, for his unwavering support, guidance, 
    and encouragement throughout the course of my research. His invaluable 
    insights and expertise have been instrumental in the completion of this thesis.

    I also extend my heartfelt thanks to the ATLAS collaboration for providing 
    the opportunity to be part of such a prestigious and groundbreaking project. 
    The resources, data, and collaborative environment have significantly contributed 
    to the advancement of my research. Thanks to all the members of the ATLAS 
    collaboration, particularly the TauCP group, for their assistance and for fostering a spirit of scientific inquiry and 
    excellence.
    
    Furthermore, I am immensely grateful to the Manchester ATLAS group for their constant 
    support and camaraderie. The collective knowledge, stimulating discussions, 
    and constructive feedback from the group have greatly enhanced my understanding 
    and have been a source of inspiration throughout my research journey.
    
    Lastly, I would like to acknowledge the support of my family and friends, 
    particularly my loving wife, for her endless patience, understanding, and 
    encouragement during the challenging times.
    
    \textbf{Thank you all for making this thesis possible!}
\end{acknowledgements}
